Daily Shelter and Overnight Services Availabilities

### 2024-09-24 paper/paper.qmd
updated some references

---
title: "Week 3 Reflection"
subtitle: "Marriage Data Cleaning"
author: "Cher Ning-Li"
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "In this paper I analyze the number of marriages across the years, from 2018-2023."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

@@

Some of our data is of marriages (@fig-marriages), from @OpenDataToronto.

>>>>

---
title: "Daily Shelter and Overnight Services Availabilities"
#subtitle: "Marriage Data Cleaning"
author: "Cher Ning-Li"
thanks: "Code and data are available at: https://github.com/cher-ning/shelter_occupancies"
date: today
date-format: long
abstract: "In this paper I analyze the capacity vs real occupancy of shelters across Canada."
#TODO Complete abstract after paper.
format: pdf
number-sections: true
bibliography: references.bib
---

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @citeTidyverse

@@

Some of our data is of marriages (@fig-marriages), from @opendatatoronto.
